\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{
  pdfauthor={},
  pdftitle={},
  pdfsubject={},
  pdfkeywords={},
  pdfcreator={},
  pdfproducer={}
}
\usepackage{setspace}
\onehalfspacing

\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\mathbb{V}\mathrm{ar}}
\newcommand{\Cov}{\mathbb{C}\mathrm{ov}}
\newcommand{\Corr}{\mathbb{C}\mathrm{orr}}
\newcommand{\SR}{\mathrm{SR}}
\newcommand{\UVIF}{\mathrm{UVIF}}
\DeclareMathOperator{\sign}{sign}

\newif\ifblinded
\ifdefined\BLINDED
  \blindedtrue
\else
  \blindedfalse
\fi

\title{Technical Appendix: Sharpe-Ratio Inference at the Date Boundary in Financial Panels}
\ifblinded
\author{}
\else
\author{Dhananjay S. Chauhan}
\fi
\date{}

\begin{document}
\maketitle

\section{Purpose}

This appendix provides derivations, calibration checks, robustness
tables, and reproducibility details omitted from the main manuscript for
brevity.  It supports the proof, calibration, and robustness record; it
is not an independent empirical claim.

\section{Mean-Return Design-Effect Proof}

For a selected row model \(y_{t,i}=\mu+\lambda_t+\epsilon_{t,i}\) with
constant selected count \(\bar n\), same-date intraclass correlation
\(\rho\), and independent dates, the row-pooled mean equals the average
of date means:
\[
  \hat\mu =
  \frac{1}{T\bar n}\sum_{t=1}^{T}\sum_{i=1}^{\bar n} y_{t,i}
  =
  \frac{1}{T}\sum_{t=1}^{T}\bar y_t .
\]
The row-naive variance report is \(\sigma^2/(T\bar n)\).  The true
one-date variance is
\[
  \Var(\bar y_t)
  =
  \frac{1}{\bar n^2}
  \{\bar n\sigma^2+\bar n(\bar n-1)\rho\sigma^2\}
  =
  \frac{\sigma^2}{\bar n}\{1+(\bar n-1)\rho\}.
\]
Thus
\[
  \frac{se_{date,true}}{se_{row,naive}}
  =
  \sqrt{1+(\bar n-1)\rho}.
\]
This is the Moulton-like design effect used as the mean-return special
case in the main text.  It is a closed-form special case, not the full
Sharpe-ratio distortion result.

\section{Sharpe UVIF Derivation}

These calculations supply the algebra behind Proposition 1 in the main
manuscript.
Let \(R_t\) be the date-level portfolio excess return and
\(G_t=(R_t,R_t^2)'\).  The annualized Sharpe ratio is the smooth
functional
\[
  f(\mu,m_2)=\sqrt{A_f}\frac{\mu}{(m_2-\mu^2)^{1/2}},
  \qquad
  d_R=\nabla f(\mu_R,m_{2,R}).
\]
The annualization factor \(A_f\) is source-specific: the public configuration
uses \(252\) for daily sources and \(12\) for monthly sources.
On sets where \(v_R=m_{2,R}-\mu_R^2>0\), the first-order expansion is
\[
  \widehat{\SR}_R-\SR_R
  =
  d_R'(\hat\theta_R-\theta_R)+o_p(T_R^{-1/2}),
  \qquad \theta_R=\E[G_t].
\]
With long-run covariance
\(\Omega_R=\Gamma_0^R+\sum_{k\ge1}(\Gamma_k^R+\Gamma_k^{R\prime})\),
\[
  \Var_{LR}(\widehat{\SR}_R)
  =
  T_R^{-1}d_R'\Omega_Rd_R+o(T_R^{-1}).
\]
The row-pooled IID calculation applies the same delta method to
\(\bar nT_R\) row observations \(H_{t,i}=(Y_{t,i},Y_{t,i}^2)'\):
\[
  \Var_{IID,row}(\widehat{\SR}_{row})
  =
  (\bar nT_R)^{-1}d_Y'\Psi_Yd_Y+o((\bar nT_R)^{-1}).
\]
Taking the ratio gives the Sharpe UVIF:
\[
  \UVIF_{\SR}
  =
  \frac{\bar n\,d_R'\Omega_Rd_R}{d_Y'\Psi_Yd_Y}
  =
  \frac{\bar n\,d_R'\Gamma_0^Rd_R}{d_Y'\Psi_Yd_Y}
  \times
  \frac{d_R'\Omega_Rd_R}{d_R'\Gamma_0^Rd_R}.
\]
The first term is the cross-sectional component and the second term is
the serial long-run factor.  Componentwise,
\[
  d_R'\Omega_Rd_R
  =
  \frac{A_f}{v_R^3}
  \left[
    m_{2,R}^2\Omega_{11}
    -\frac{\mu_Rm_{2,R}}{2}(\Omega_{12}+\Omega_{21})
    +\frac{\mu_R^2}{4}\Omega_{22}
  \right].
\]
The \(\Omega_{22}\) term contains long-run covariances of squared
returns and therefore brings fourth moments into Sharpe-ratio variance.

\section{Optional Square-Root Impact Sensitivity}

The public sorted-portfolio examples in the main manuscript do not
contain average daily volume or order-size information, so they do not
support a capacity claim.  For traded-security panels where those inputs
are available, a square-root impact diagnostic can be added as an
optional sensitivity extension.

\begin{proposition}[Square-root impact sensitivity bound]
\label{prop:capacity-frontier}
Suppose a traded panel has row-pooled gross mean \(\bar r_{\mathrm{gross}}\),
row-pooled return standard deviation \(\sigma_{\mathrm{row}}\),
strictly positive average turnover \(\widehat{\mathrm{TO}}\), \(T\)
trading dates, square-root impact cost
\(\lambda \widehat{\mathrm{TO}}\sqrt{A/V}\), and a dependence
standard-error inflation factor \(\mathcal M\ge 1\) relative to
row-pooled inference.
For a one-sided level-\(\alpha\) sensitivity margin, any statistically
screened asset scale \(A^*\) must satisfy
\begin{equation}
  A^*
  \le
  V\left(
    \frac{\bar r_{\mathrm{gross}}
      -z_{\alpha}\mathcal M\sigma_{\mathrm{row}}/\sqrt{T}}
         {\lambda \widehat{\mathrm{TO}}}
  \right)^2
  \label{eq:capacity-frontier}
\end{equation}
when the numerator is positive; otherwise no positive scale is screened
by the margin.
\end{proposition}

For a square-root impact diagnostic, the dependence-adjusted one-sided
lower confidence margin for gross mean return is
\[
  \bar r_{\mathrm{gross}}
  - z_{\alpha}\mathcal M\sigma_{\mathrm{row}}/\sqrt{T},
\]
where \(\sigma_{\mathrm{row}}\) is the standard deviation of row-pooled
returns before date aggregation or UVIF adjustment.  Square-root impact
subtracts \(\lambda\widehat{\mathrm{TO}}\sqrt{A/V}\).  Requiring the net lower
margin to be nonnegative gives
\[
  \lambda\widehat{\mathrm{TO}}\sqrt{A/V}
  \le
  \bar r_{\mathrm{gross}}
  - z_{\alpha}\mathcal M\sigma_{\mathrm{row}}/\sqrt{T}.
\]
Rearranging yields the sensitivity bound in Proposition
\ref{prop:capacity-frontier}.  If
the volatility input is already the date-level portfolio volatility, the
date boundary has already embedded the cross-sectional UVIF component,
so the cross-sectional part of \(\mathcal M\) must not be multiplied in
again.

\section{Higher-Moment UVIF and ERIR Details}

For \(\theta^{(4)}=(\mu,m_2,m_3,m_4)'\), define skewness and kurtosis
from the central moments implied by \(\theta^{(4)}\).  Any adjusted
Sharpe functional \(h(\theta^{(4)})\) has a delta-method variance
\(\nabla h'\Omega^{(4)}\nabla h\), where \(\Omega^{(4)}\) is the
long-run covariance matrix of \((R_t,R_t^2,R_t^3,R_t^4)'\).  The
higher-moment UVIF is the corresponding ratio of date-level long-run
variance to row-pooled IID variance.  It is a diagnostic extension, not
an additional empirical rejection rule.

The Effective Row Information Retention (ERIR) diagnostic is a
design-effect retention calculation, not a hypothesis test or a formal
information claim.  Under the same equicorrelated approximation
used for the mean-return design effect,
\[
  DE_{\mu,xs}=1+(\bar n-1)\rho,
  \qquad
  \mathrm{ERIR}=\{1+(\bar n-1)\rho\}^{-1}.
\]
Thus an ERIR of \(0.111\) means that roughly \(1-0.111=0.889\), or 89
percent, of nominal row-level information is redundant under this
diagnostic approximation.  Confirmatory inference remains based on
date-level HAC-delta and dependent-bootstrap procedures.  When the
descriptive equicorrelation estimate is non-positive, the unclipped ERIR
can exceed one and the corresponding UVIF can fall below one; the main
manuscript displays a conservative one-sided UVIF floor at one and
reports the unclipped diagnostics separately.

\section{Synthetic Positive Control}

This section gives the appendix version of the known-edge calibration
check.  The synthetic panel is not empirical evidence for a public
strategy; it verifies that the pre-specified reporting rule can
accept a declared positive signal when the data-generating process
contains one.
The generated panel has \(T=5000\) dates and \(N=100\) names.  Signed
returns include daily alpha \(0.12/252\), idiosyncratic volatility
\(0.01\), a common loading of \(0.50\), AR(1) common-factor coefficient
\(0.10\), signal-stay probability \(0.98\), and seed 777.  The displayed
run is one representative known-edge calibration with 5000 bootstrap
draws and 10000 same-date permutations; costs use the same 5 bps
turnover-stress convention as the public tables.  The replication
screen below uses fewer resampling draws and is reported only as a power
sanity check.
The data-generating process is
\[
  f_t = 0.10 f_{t-1}+u_t,\qquad
  \epsilon_{t,i}\sim N(0,0.01^2),
\]
\[
  z_{t,i}\in\{-1,1\},\qquad
  \Pr(z_{t,i}=z_{t-1,i})=0.98,
\]
\[
  r_{t+1,i}=z_{t,i}(0.12/252)+0.50 f_t+\epsilon_{t,i},
  \qquad s_{t,i}=z_{t,i}.
\]
The calibration then applies the same signed-row construction, date
aggregation, HAC-delta inference, Romano-Wolf menu adjustment,
same-date permutation, and 5 bps cost stress used in the public tables.

\input{generated_positive_control_artifacts.tex}

\section{Full Empirical Tables}

These tables are supporting diagnostics rather than primary evidence; the main text
reports the compressed interpretation.
The inferential tables in this appendix report only public sources that
loaded and produced reproducible outputs.  Failed source-access
attempts remain in the generated provenance files and run metadata,
but are not treated as empirical evidence.
Panel candidates and pre-aggregated factor benchmarks are reported in
separate groups because only the former provide row-level signals for
same-date permutation and sampling-boundary diagnostics.
For each empirical table group, the check is whether the result survives
moving from rows to date returns, whether nearby HAC and dependent-bootstrap
variants agree, and whether placebo or cost diagnostics overturn the simple
Sharpe interpretation.  Large disagreement across these tables is a
robustness warning, not a new discovery channel.

\input{generated_empirical_artifacts.tex}

\section{Full Monte Carlo Tables}

The simulation tables target the date-level Sharpe claim.  Row-naive
coverage is therefore reported against that date-level target, not
against a separate row-distribution target.  The design-sweep table is a
stress diagnostic over same-date correlation and selected-count pressure
under a zero-edge null.
The main concern in this table group is size distortion: a method that
looks powerful because it overrejects under the null is not acceptable
for confirmatory evaluation.

\input{generated_simulation_artifacts.tex}

\section{Robustness and Configuration Notes}

The public configuration is fixed in \path{code/campaign_registry.json}.  It
records loaders, public source metadata, threshold menus, primary
thresholds, and lookback/skip parameters.  Changing a source, lookback,
threshold, cost assumption, or eligibility rule after seeing results
creates a new researcher menu and must be reported as exploratory.
Rendered tables in the submitted package use the following SHA256
identifiers:
\begin{quote}\scriptsize
\noindent configuration \texttt{code/campaign\_registry.json}:\\
\texttt{3a616f119f3fe2603b0663e3f68c499496c37a1781f3003e82814c9269a16259}\\
\noindent generated campaign metadata \texttt{campaign\_metadata.json}:\\
\texttt{5cb21ac2cb87cb74a26090a66b28dac6890f76dd1d4bd4391ea6290267810dff}
\end{quote}

Stationarity diagnostics, holdout splits, HAC bandwidth sweeps,
prewhitened HAC, fixed-fraction HAC, moving-block bootstrap, and
stationary bootstrap results are secondary robustness checks.  They are
used to identify fragile claims, not to replace the main date-return
decision rule.

\end{document}
